\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-15 paper.tex
Updated charts

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figures/mean-far-by-electrode-config.png}
\caption{FAR by electrode configuration. All electrodes combined achieves a perfect score. We achieve the next best scores using data from the left ear only.}
\label{fig:meanByElectrode}
\end{figure}

@@

All best-performing tasks in our best-case set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (breathe) had a nonzero FRR.
Breathe appeared as the best task across all participants. Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants.
This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did /Song (eyes open)/ and /sport/ (though, interestingly, song with eyes closed performed less well).

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figures/mean-far-by-task.png}
\caption{FAR in the left ear by task, across all subjects.}
\label{fig:meanByTask}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-electrode-config.png}
\caption{FAR by electrode configuration. All electrodes combined achieves a perfect score. We achieve the next best scores using data from the left ear only.}
\label{fig:meanByElectrode}
\end{figure}

@@

All best-performing tasks in our best-case set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (breathe) had a nonzero FRR.
Breathe appeared as the best task across all participants. Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants.
This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did song (eyes open) and sport (though, interestingly, song with eyes closed performed less well).

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figures/mean-far-and-frr-by-task.png}
\caption{FAR by task, across all subjects, using data from the left ear only.}
\label{fig:meanByTask}
\end{figure}
